Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-06-13 man/figures/resilience_long_term.Rmd
update figures

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
library("broom")
```

@@

```{r plot_join}
res_long_term <- sevRt + sevRc + sevRs + 
  plot_layout(nrow = 1) 
```

@@

```{r plot_out, fig.width=6, dpi = 300, out.width = 0.8}
res_long_term
```

```{r, eval=FALSE, echo=FALSE}
df <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))

nested_df <- group_by(df, res_metric) %>% nest()

fit_model <- function(df){
  lm(value ~ d_severity, data = df)
}

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label, 
                        colour = site, fill = site)) + 
    geom_smooth(method='lm', se=FALSE) + 
    geom_point(size=1.5, pch = 21) + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3) + 
    annotate("text", x = coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE, 
             size = 3, fontface = "bold", hjust="left") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10)) +
    geom_text_repel(data = eqns, aes(x = -Inf, y = Inf,label = equation), parse = TRUE, segment.size = 0)

@@

plotrelsite(sdfsite, v = "rs", x = 'd_severity', label = 'disturb_year',
                 site = "site",
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') + 
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))

@@

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
library("broom")
library("cowplot")
```

@@

```{r plot_join, eval=FALSE, echo=FALSE}
res_long_term <- sevRt + sevRc + sevRs + 
  plot_layout(nrow = 1) 
```

@@

```{r plot_out, fig.width=6, dpi = 300, out.width = 0.8, eval=FALSE, echo=FALSE}
res_long_term
```

```{r, eval=FALSE, echo=FALSE}
dff <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))

nested_df <- group_by(dff, res_metric) %>% nest()

fit_model <- function(x){
  lm(value ~ d_severity, data = x)
}

@@

  ggplot(df, 
         aes_string(y=paste0(v, "_mean_mean"), x=x, label=label, colour=site, fill=site)) +
    geom_smooth(method='lm', se=FALSE, aes(group=1), colour='black', linetype = "dashed", size = 1) +
    geom_smooth(method='lm', se=FALSE) + 
    geom_point(size=1.5, pch = 21) + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 3, show.legend = FALSE) + 
    # annotate("text", x = coordX_eq, y = coordY_eq, 
    #          label=lm_eqn(lm(formulita, df)), parse=TRUE, 
    #          size = 3, fontface = "bold", hjust="left") +
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10)) +
    geom_text_repel(data = eqns, aes(x = -Inf, y = Inf, label = equation), 
                    direction = "y", 
                    parse = TRUE, segment.size = 0, show.legend = FALSE)

@@

@@

```{r}
sevRt_site <- plotrelsite(sdfsite, v = "rt", x = 'd_severity', label = 'disturb_year', site = "site",
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))
```

```{r}
sevRs_site <- plotrelsite(sdfsite, v = "rs", x = 'd_severity', label = 'disturb_year', site = "site",
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') + theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt")) 
```

```{r}
sevRc_site <- plotrelsite(sdfsite, v = "rc", x = 'd_severity', label = 'disturb_year', site = "site",
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab("") +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```

```{r}
res_long_term_sites <- sevRt_site + theme(legend.position="none") +
  sevRc_site + theme(legend.position="bottom") +
  sevRs_site + theme(legend.position = "none") + plot_layout(nrow = 1)

ggsave(filename = here::here("./man/figures/svg/fig_6.jpg"), 
       dpi = 300,  plot=res_long_term_sites, width=10, height=8)

```{r, fig.width=6, dpi = 300, out.width = 0.8}
res_long_term_sites
```
